---
title: "STA207_Final_Report"
author: "ChiChun-Chen"
date: "2026-03-03"
output: html_document
---

# ---- Extract Stayers Table ----

## 1. Setup

```{r setup, include=TRUE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/chichichen/Documents/Master/5-2026Winter/STA 207/Final_Project")
# ---- 1. Packages ----
pkgs <- c("haven","dplyr","tidyr","ggplot2","skimr","janitor","GGally",
          "data.table","plotly","stringr","broom","sandwich","lmtest",
          "ggalluvial", "forcats", "scales", "purrr", "tibble")
to_install <- pkgs[!pkgs %in% installed.packages()[,"Package"]]
if(length(to_install)>0) install.packages(to_install)
invisible(lapply(pkgs, library, character.only = TRUE))

# ---- 2. Import data ----
# setwd("/Users/chichichen/Documents/Master/5-2026Winter/STA 207/Final_Project")
df <- read_sav("../STAR_Students.sav") %>% janitor::clean_names()
cat("Total data count:", nrow(df), "\n\n")

# ---- 3. Variable maps ----
map_long <- list(
  class      = c(k="gkclasstype"),
  school_id  = c(k="gkschid"),
  teacher_id = c(k="gktchid"),
  freelunch  = c(k="gkfreelunch"),
  race   = "race"
)

# ---- 4. Keep only existing columns ----
keep_exist <- function(x, data = df) {
  x[x %in% names(data)]
}

predictor_vars <- map_long %>%
  unlist(use.names = FALSE) %>%
  unique() %>%
  keep_exist(df)

outcome <- "gktmathss"

# ---- 5. Build a new dataframe with all selected variables + outcome ----
analysis_vars <- c(predictor_vars, outcome) %>%
  unique() %>%
  keep_exist(df)

df_analysis <- df %>%
  dplyr::select(all_of(analysis_vars))

# convert factor
df_analysis <- df_analysis %>%
  mutate(across(c("gkclasstype"), as.factor))

# drop rows with missing outcome or missing teacher ID
df_analysis <- df_analysis %>%
  dplyr::filter(!is.na(gktmathss), !is.na(gktchid), !is.na(gkfreelunch))

# check result
glimpse(df_analysis)
names(df_analysis)
```
```{r}
library(dplyr)
library(ggplot2)
library(forcats)

df_plot <- df %>%
  filter(!is.na(gkschid), !is.na(gktmathss)) %>%
  group_by(gkschid) %>%
  mutate(school_median = median(gktmathss, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(gkschid = fct_reorder(as.factor(gkschid), school_median))

ggplot(df_plot, aes(x = gkschid, y = gktmathss, fill = school_median)) +
  geom_boxplot(outlier.alpha = 0.4) +
  coord_flip() +
  labs(
    title = "Distribution of Kindergarten Math Scores by School",
    x = "School ID",
    y = "Kindergarten Total SAT Math Score",
    fill = "School median"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 6),
    plot.title = element_text(face = "bold")
  )

```
```{r}
library(dplyr)
library(ggplot2)
library(forcats)

df_plot <- df %>%
  filter(!is.na(gkschid), !is.na(gktmathss)) %>%
  group_by(gkschid) %>%
  mutate(school_median = median(gktmathss, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(gkschid = fct_reorder(as.factor(gkschid), school_median))

ggplot(df_plot, aes(x =gktmathss , y = gkschid , fill = school_median)) +
  geom_boxplot(outlier.alpha = 0.4) +
  coord_flip() +
  scale_fill_gradientn(
    colors = c("red", "orange", "yellow", "green", "blue", "purple")
  ) +
  labs(
    title = "Distribution of Kindergarten Math Scores by School",
    x = "Kindergarten Total SAT Math Score",
    y ="School ID" ,
    fill = "School median"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90,size=5),
    axis.text.y = element_text(size = 6),
    plot.title = element_text(face = "bold"),
    legend.position = "none"
  )
```

## 2. [EDA] Free lunch eligibility


```{r}
# count
df_analysis %>%
  count(gkfreelunch)

# proportion
df_analysis %>%
  count(gkfreelunch) %>%
  mutate(prop = n / sum(n))

# Freelunch classtype
df_analysis %>%
  ggplot(aes(x = gkclasstype, fill = gkfreelunch)) +
  geom_bar(position = "dodge") +
  geom_text(
    stat = "count",
    aes(label = after_stat(count)),
    position = position_dodge(width = 0.9),
    vjust = -0.3
  ) +
  labs(
    title = "Free Lunch Eligibility by Class Type",
    x = "Class Type",
    y = "Count",
    fill = "Free Lunch"
  ) +
  theme_minimal()
```

## 3. Free Lunch Box plot

```{r}
df_analysis %>%
  filter(!is.na(gkfreelunch), !is.na(gktmathss)) %>%
  mutate(gkfreelunch = factor(gkfreelunch, levels = c(1, 2), labels = c("Free Lunch", "No Free Lunch"))) %>%
  ggplot(aes(x = gkfreelunch, y = gktmathss, fill = gkfreelunch)) +
  geom_boxplot() +
  labs(
    title = "Boxplot of Kindergarten Math Score by Free Lunch Status",
    x = "Free Lunch Status",
    y = "Kindergarten Total Math Score"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```
## 4. Free Lunch Violent plot

```{r}
df_analysis %>%
  filter(!is.na(gkfreelunch), !is.na(gktmathss)) %>%
  mutate(gkfreelunch = factor(gkfreelunch, levels = c(1, 2), labels = c("Free Lunch", "No Free Lunch"))) %>%
  ggplot(aes(x = gkfreelunch, y = gktmathss, fill = gkfreelunch)) +
  geom_boxplot() +
  labs(
    title = "Boxplot of Kindergarten Math Score by Free Lunch Status",
    x = "Free Lunch Status",
    y = "Kindergarten Total Math Score"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

## 4. TeacherID

```{r}
Teacher_Stats <- df %>%
  group_by(gktchid) %>%
  summarise(
    mean = round(mean(gktmathss, na.rm = T), 1),
    median = median(gktmathss, na.rm = T),
    min = min(gktmathss, na.rm = T),
    max = max(gktmathss, na.rm = T),
    Q1 = round(quantile(gktmathss, 0.25, na.rm = T), 1),
    Q3 = round(quantile(gktmathss, 0.75, na.rm = T), 1)
  )

Teacher.Stats.Head = head(Teacher_Stats, 10)
Teacher.Stats.Head

Teacher.Stats.Table = kable(Teacher.Stats.Head, "html") %>% 
  kable_styling("striped", full_width = F)

save_kable(Teacher.Stats.Table, file = "Teacher_Stats_Table.png")


```

## 5. Box-Plot of three class type SAT math score

```{r}
boxplot(gktmathss ~ gkclasstype, data = df_analysis)
```

# ---- [F-test] Classtype outcome score ----

```{r}
fit <- aov(gktmathss ~ gkclasstype, data = df_analysis)
summary(fit)
```
# ---- [T-test] Regular vs Regular+Aid ----

```{r}
df_23 <- df_analysis %>%
  dplyr::filter(gkclasstype %in% c(2, 3), !is.na(gktmathss)) %>%
  dplyr::mutate(gkclasstype = droplevels(as.factor(gkclasstype)))

table(df_13$gkclasstype)

t.test(gktmathss ~ gkclasstype, data = df_23)
```



# ---- NO NEED TO USE ----

```{r}
na_check_function <- function(data,
                              group_col = "classtype",
                              vars = NULL,
                              add_total = TRUE,
                              include_type = TRUE,
                              include_rate = FALSE,
                              group_levels = c("1","2","3","Total")) {
  stopifnot(is.data.frame(data))
  if(!group_col %in% names(data)) stop("group_col not found in data: ", group_col)

  if(is.null(vars)) {
    vars <- setdiff(names(data), group_col)
  } else {
    vars <- intersect(vars, names(data))
  }

  # NA count for each group
  na_4x24 <- data %>%
    mutate(.group = as.character(.data[[group_col]])) %>%
    group_by(.group) %>%
    summarise(across(all_of(vars), ~ sum(is.na(.x))), .groups = "drop") %>%
    rename(!!group_col := .group)

  # Total row
  if(add_total) {
    na_total <- data %>%
      summarise(across(all_of(vars), ~ sum(is.na(.x)))) %>%
      mutate(!!group_col := "Total") %>%
      select(all_of(group_col), everything())

    na_4x24 <- bind_rows(na_4x24, na_total)
  }

  na_24x4 <- na_4x24 %>%
    tibble::column_to_rownames(group_col) %>%
    t() %>%
    as.data.frame(check.names = FALSE) %>%
    tibble::rownames_to_column("variable")

  if(!is.null(group_levels)) {
    missing_cols <- setdiff(group_levels, names(na_24x4))
    for(mc in missing_cols) na_24x4[[mc]] <- 0
    na_24x4 <- na_24x4 %>% select(variable, any_of(group_levels), everything())
  }

  # Add type column
  if(include_type) {
    type_tbl <- tibble::tibble(
      variable = vars,
      type = sapply(data[vars], function(x) paste(class(x), collapse = "/"))
    )
    na_24x4 <- na_24x4 %>% left_join(type_tbl, by = "variable")
  }

  # NA rate
  if(include_rate) {
    n_by_group <- data %>%
      mutate(.group = as.character(.data[[group_col]])) %>%
      count(.group, name = "n") %>%
      rename(!!group_col := .group)

    n_total <- nrow(data)
    if(add_total) {
      n_by_group <- bind_rows(n_by_group, tibble::tibble(!!group_col := "Total", n = n_total))
    }

    n_vec <- setNames(n_by_group$n, n_by_group[[group_col]])
    grp_cols <- setdiff(names(na_24x4), c("variable","type","base_type","is_labelled"))
    grp_cols <- intersect(names(n_vec), grp_cols)

    na_24x4[ "NA_rate"] <- round(na_24x4[["Total"]] / n_vec[["Total"]], 4)
  }

  na_24x4
}

vars_24 <- setdiff(names(df_analysis), "classtype")
na_check_function(df_analysis, group_col = "classtype", vars = vars_24,
                              include_type = TRUE, include_rate = TRUE)
```

We only need to deal with "gkfreelunch", "g1freelunch", "g2freelunch", "g3freelunch", "gktyears", "g1tyears" ,"g2tyears", "g3tyears"

## Functions for filling missing values

```{r}
to01_function <- function(x){
  ifelse(x == 1, 1, ifelse(x == 2, 0, NA))
}
back12_function <- function(p){
  ifelse(p >= 0.5, 1, 2)
}
# ---------- Helper-freelunch ----------
impute_freelunch_glm_function <- function(data, target, predictors, min_complete = 30){
  use_preds <- intersect(setdiff(predictors, target), names(data))

  d <- data %>% dplyr::mutate(y = to01_function(.data[[target]]))
  test_idx <- which(is.na(d$y))
  if(length(test_idx) == 0) return(data)

  model_df <- d %>%
    dplyr::filter(!is.na(y)) %>%
    dplyr::select(y, dplyr::all_of(use_preds)) %>%
    tidyr::drop_na()

  # fallback: mode
  mode_val <- d %>%
    dplyr::filter(!is.na(.data[[target]])) %>%
    dplyr::count(.data[[target]], sort = TRUE) %>%
    dplyr::slice(1) %>%
    dplyr::pull(1)

  if(nrow(model_df) < min_complete){
    warning(paste("Too few complete cases for", target, "- fallback to mode"))
    data[[target]][test_idx] <- mode_val
    return(data)
  }

  fit <- glm(y ~ ., data = model_df, family = binomial())

  newdata <- d %>% dplyr::slice(test_idx) %>% dplyr::select(dplyr::all_of(use_preds))
  p <- suppressWarnings(predict(fit, newdata = newdata, type = "response"))

  imputed <- back12_function(p)
  imputed[is.na(imputed)] <- mode_val

  data[[target]][test_idx] <- imputed
  data
}

# ---------- Helper-tyears ----------
impute_continuous_lm_function <- function(data, target, predictors, min_complete = 30, seed = 123){
  use_preds <- intersect(setdiff(predictors, target), names(data))

  idx <- which(is.na(data[[target]]))
  if(length(idx) == 0) return(data)

  train <- data %>%
    dplyr::select(dplyr::all_of(c(target, use_preds))) %>%
    tidyr::drop_na()

  if(nrow(train) < min_complete){
    warning(paste("Too few complete cases for", target, "- fallback to median"))
    med <- median(data[[target]], na.rm = TRUE)
    data[[target]][idx] <- as.integer(round(med))
    return(data)
  }

  fit <- lm(reformulate(use_preds, response = target), data = train)
  resid_pool <- residuals(fit)

  newdata <- data[idx, use_preds, drop = FALSE]
  pred <- predict(fit, newdata = newdata)

  set.seed(seed)
  noise <- sample(resid_pool, size = length(pred), replace = TRUE)

  imputed <- pred + noise
  imputed <- pmax(imputed, 0)               
  imputed <- as.integer(round(imputed))    

  data[[target]][idx] <- imputed
  data
}

# ---------- Main pipeline ----------
impute_star_covariates_function <- function(data,
                                   freelunch_targets = c("gkfreelunch","g1freelunch","g2freelunch","g3freelunch"),
                                   tyears_targets    = c("gktyears","g1tyears","g2tyears","g3tyears"),
                                   seed = 123){

  pred_pool_common <- c(
    "gender","race","classtype",
    "gksurban","g1surban","g2surban","g3surban",
    "gktmathss","g1tmathss","g2tmathss"
  )

  # 1. freelunch imputation
  preds_lunch <- intersect(c(pred_pool_common, freelunch_targets), names(data))
  out <- data
  for(tgt in intersect(freelunch_targets, names(out))){
    out <- impute_freelunch_glm_function(out, tgt, preds_lunch, min_complete = 30)
  }

  # 2. tyears imputation (after freelunch, so SES predictors are more complete)
  preds_tyears <- intersect(c(pred_pool_common, tyears_targets, freelunch_targets), names(out))
  for(tgt in intersect(tyears_targets, names(out))){
    out <- impute_continuous_lm_function(out, tgt, preds_tyears, min_complete = 30, seed = seed)
  }

  out
}
```

## Fill in missing values

```{r}
df_stayers_imp <- impute_star_covariates_function(df_stayers, seed = 123)

na_after <- na_check_function(df_stayers_imp, group_col="classtype", vars=vars_24,
                              include_type=TRUE, include_rate=TRUE)

na_after %>% filter(variable %in% c("gkfreelunch","g1freelunch","g2freelunch","g3freelunch",
                                   "gktyears","g1tyears","g2tyears","g3tyears"))

```

## Filtered NA value

```{r}
df_stayers <- df_stayers_imp %>%
  filter(!is.na(g3tmathss))
na_check_function(df_stayers, group_col="classtype", vars=vars_24,
                              include_type=TRUE, include_rate=TRUE)
write.csv(df_stayers, "df_stayers_final.csv", row.names = TRUE)
```

## EDA all variables

```{r}
vars <- c(
  "gkschid","g1schid","g2schid","g3schid",
  "gktchid","g1tchid","g2tchid","g3tchid",
  "gkfreelunch","g1freelunch","g2freelunch","g3freelunch",
  "gksurban","g1surban","g2surban","g3surban",
  "gktyears","g1tyears","g2tyears","g3tyears",
  "gender","race","g3tmathss","classtype"
)
vars <- intersect(vars, names(df_stayers))

df_eda <- df_stayers %>%
  select(all_of(vars)) %>%
  mutate(classtype = as.factor(classtype))

# Helper: grade labels
grade_map <- function(x){
  recode(x,
         gk="K", g1="G1", g2="G2", g3="G3",
         gks="K", g1s="G1", g2s="G2", g3s="G3")
}

# ---- 1. Overall column audit ----
col_audit <- tibble(
  variable = names(df_eda),
  type = sapply(df_eda, \(x) paste(class(x), collapse="/")),
  base_type = sapply(df_eda, typeof),
  n = nrow(df_eda),
  n_miss = sapply(df_eda, \(x) sum(is.na(x))),
  miss_rate = round(n_miss / n, 4),
  n_unique_nonmiss = sapply(df_eda, \(x) dplyr::n_distinct(x, na.rm = TRUE))
) %>% arrange(desc(miss_rate), desc(n_miss))

col_audit
# knitr::kable(col_audit, digits = 4)

# ---- 2. Missingness by classtype (for causal balance / data quality) ----
miss_by_classtype <- df_eda %>%
  group_by(classtype) %>%
  summarise(across(everything(), ~ round(mean(is.na(.x)), 4)), .groups = "drop")

miss_by_classtype
# knitr::kable(miss_by_classtype, digits = 4)

# ----  freelunch & surban ----
make_long_cat <- function(data, cols, value_name){
  data %>%
    select(classtype, all_of(cols)) %>%
    pivot_longer(cols = all_of(cols), names_to = "var", values_to = value_name) %>%
    mutate(
      grade = case_when(
        grepl("^gk", var) ~ "K",
        grepl("^g1", var) ~ "G1",
        grepl("^g2", var) ~ "G2",
        grepl("^g3", var) ~ "G3",
        TRUE ~ var
      )
    )
}

# ---- 3.Free lunch by grade (proportion) ----
lunch_cols <- intersect(c("gkfreelunch","g1freelunch","g2freelunch","g3freelunch"), names(df_eda))

df_lunch_long <- make_long_cat(df_eda, lunch_cols, "freelunch") %>%
  mutate(
    freelunch = factor(freelunch, levels = c(1,2), labels = c("Free lunch","Non-free"))
  )

lunch_sum <- df_lunch_long %>%
  count(grade, freelunch) %>%
  group_by(grade) %>%
  mutate(pct = n/sum(n)) %>%
  ungroup()

ggplot(lunch_sum, aes(x = grade, y = pct, fill = freelunch)) +
  geom_col(width = 0.7) +
  scale_y_continuous(labels = percent) +
  labs(title = "Free lunch rate by grade", x = "Grade", y = "Proportion", fill = NULL) +
  theme_minimal()

# Free lunch by grade (counts) 
ggplot(lunch_sum, aes(x = grade, y = n, fill = freelunch)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent(pct, accuracy = 0.1)),
            position = position_stack(vjust = 0.5), size = 3.5) +
  labs(title = "Free lunch counts by grade", x = "Grade", y = "Count", fill = NULL) +
  theme_minimal()

# Free lunch switch rate across grades
switch_rate <- function(data, v1, v2, name){
  data %>%
    filter(!is.na(.data[[v1]]), !is.na(.data[[v2]])) %>%
    summarise(
      pair = name,
      n = n(),
      n_switch = sum(.data[[v1]] != .data[[v2]]),
      switch_rate = round(n_switch / n, 4)
    )
}

if(length(lunch_cols) == 4){
  bind_rows(
    switch_rate(df_eda, "gkfreelunch","g1freelunch","K→G1"),
    switch_rate(df_eda, "g1freelunch","g2freelunch","G1→G2"),
    switch_rate(df_eda, "g2freelunch","g3freelunch","G2→G3")
  )
}

# ---- 3. Surban by grade (proportion) ----
urban_cols <- intersect(c("gksurban","g1surban","g2surban","g3surban"), names(df_eda))
df_urban_long <- make_long_cat(df_eda, urban_cols, "surban") %>%
  mutate(surban = as.factor(surban))

urban_sum <- df_urban_long %>%
  count(grade, surban) %>%
  group_by(grade) %>%
  mutate(pct = n/sum(n)) %>%
  ungroup()

ggplot(urban_sum, aes(x = grade, y = pct, fill = surban)) +
  geom_col(width = 0.7) +
  scale_y_continuous(labels = percent) +
  labs(title = "Urbanicity (surban) distribution by grade", x = "Grade", y = "Proportion", fill = NULL) +
  theme_minimal()

# ---- 4. Continuous longitudinal EDA: tyears ----
tyears_cols <- intersect(c("gktyears","g1tyears","g2tyears","g3tyears"), names(df_eda))

df_tyears_long <- df_eda %>%
  select(classtype, all_of(tyears_cols)) %>%
  pivot_longer(cols = all_of(tyears_cols), names_to = "var", values_to = "tyears") %>%
  mutate(
    grade = case_when(
      grepl("^gk", var) ~ "K",
      grepl("^g1", var) ~ "G1",
      grepl("^g2", var) ~ "G2",
      grepl("^g3", var) ~ "G3",
      TRUE ~ var
    )
  )

# Summary table by grade
tyears_summary <- df_tyears_long %>%
  group_by(grade) %>%
  summarise(
    n = sum(!is.na(tyears)),
    mean = mean(tyears, na.rm = TRUE),
    sd = sd(tyears, na.rm = TRUE),
    median = median(tyears, na.rm = TRUE),
    p25 = quantile(tyears, 0.25, na.rm = TRUE),
    p75 = quantile(tyears, 0.75, na.rm = TRUE),
    .groups = "drop"
  )

tyears_summary
# knitr::kable(tyears_summary, digits = 3)

# Boxplot by grade
ggplot(df_tyears_long, aes(x = grade, y = tyears)) +
  geom_boxplot() +
  labs(title = "Teacher years of experience (tyears) by grade", x = "Grade", y = "tyears") +
  theme_minimal()

# Boxplot by classtype (using G3 tyears as example if available)
if("g3tyears" %in% names(df_eda)){
  ggplot(df_eda, aes(x = classtype, y = g3tyears, fill = classtype)) +
    geom_boxplot(show.legend = FALSE) +
    labs(title = "G3 teacher years (g3tyears) by class type", x = "Class type", y = "g3tyears") +
    theme_minimal()
}

# ---- 5. Demographics: gender / race ----
if("race" %in% names(df_eda)){

  df_eda2 <- df_eda %>%
    mutate(
      race_bin = case_when(
        is.na(race) ~ NA_character_,
        race == 1 ~ "White",
        TRUE ~ "Other"
      ) %>% factor(levels = c("White","Other"))
    )

  # Overall distribution
  df_eda2 %>%
    count(race_bin, name = "n") %>%
    ggplot(aes(x = race_bin, y = n, fill = race_bin)) +
    geom_col(show.legend = FALSE) +
    geom_text(aes(label = n), vjust = -0.3, size = 4) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
    labs(title = "Race (binary): White vs Other", x = "Race", y = "Count") +
    theme_minimal()

  # By classtype (proportion)
  df_eda2 %>%
    count(classtype, race_bin, name = "n") %>%
    group_by(classtype) %>%
    mutate(pct = n/sum(n)) %>%
    ungroup() %>%
    ggplot(aes(x = classtype, y = pct, fill = race_bin)) +
    geom_col(position = "fill", width = 0.7) +
    scale_y_continuous(labels = percent) +
    labs(title = "Race (White vs Other) by class type", x = "Class type", y = "Proportion", fill = NULL) +
    theme_minimal()
}

# ---- 6. Outcome: g3tmathss ----
if("g3tmathss" %in% names(df_eda)){
  ggplot(df_eda, aes(x = g3tmathss)) +
    geom_histogram(bins = 30) +
    labs(title = "Distribution of g3tmathss", x = "g3tmathss", y = "Count") +
    theme_minimal()

  ggplot(df_eda, aes(x = classtype, y = g3tmathss, fill = classtype)) +
    geom_boxplot(show.legend = FALSE) +
    labs(title = "g3tmathss by class type", x = "Class type", y = "g3tmathss") +
    theme_minimal()

  df_eda %>%
    group_by(classtype) %>%
    summarise(
      n = sum(!is.na(g3tmathss)),
      mean = mean(g3tmathss, na.rm = TRUE),
      sd = sd(g3tmathss, na.rm = TRUE),
      .groups = "drop"
    )
}

# ---- 7. IDs: school/teacher ----
top_freq <- function(x, k = 10){
  tibble(val = x) %>%
    filter(!is.na(val)) %>%
    count(val, sort = TRUE) %>%
    slice(1:k)
}

id_cols <- intersect(c("gkschid","g1schid","g2schid","g3schid","gktchid","g1tchid","g2tchid","g3tchid"), names(df_eda))

id_summary <- tibble(
  variable = id_cols,
  n_unique = sapply(df_eda[id_cols], \(x) n_distinct(x, na.rm = TRUE)),
  miss_rate = sapply(df_eda[id_cols], \(x) round(mean(is.na(x)), 4))
)

id_summary
# knitr::kable(id_summary, digits = 4)

# Example: show top 10 schools in G3 (if exists)
if("g3schid" %in% names(df_eda)){
  top_freq(df_eda$g3schid, k = 10)
}
```
